Manuscript Figures

### 2018-05-31 Manuscript Figures.Rmd
Attempting to put correlation values in faceted graphs

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
plot(plot)

@@

## View as scatter
ggplot(data, aes(FPKM_maize1, dNSAF_maize1)) +
  geom_point(alpha=.1) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  # geom_smooth(method="loess", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  facet_wrap(~sample, nrow=6) +
  labs(
    title = paste0("Scatterplot of Expression in Maize1 vs. Abundance in Maize1\nLog-Log Scale for gene pair(s).\nAlpha=.1, reference line (black), lm fit (blue)"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Abundance for Maize1 Gene (log scale)"
  )

>>>>

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
  # + annotate("text", size=2, x=10000,y=10, label=paste("pearson: ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(plot)

@@

## View as scatter
ggplot(data, aes(FPKM_maize1, dNSAF_maize1)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  # geom_smooth(method="loess", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
  labs(
    title = paste0("Scatterplot of Expression in Maize1 vs. Abundance in Maize1\nLog-Log Scale for gene pair(s).\nAlpha=.1, reference line (black), lm fit (blue)"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Abundance for Maize1 Gene (log scale)"
  )
